--- 
title: "A Minimal Book Example"
author: "Yihui Xie"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
output: bookdown::gitbook
documentclass: book
bibliography: [book.bib, packages.bib]
biblio-style: apalike
link-citations: yes
github-repo: rstudio/bookdown-demo
description: "This is a minimal example of using the bookdown package to write a book. The output format for this example is bookdown::gitbook."
---

# Prerequisites

This is a _sample_ book written in **Markdown**. You can use anything that Pandoc's Markdown supports, e.g., a math equation $a^2 + b^2 = c^2$.

The **bookdown** package can be installed from CRAN or Github:

```{r eval=FALSE}
install.packages("bookdown")
# or the development version
# devtools::install_github("rstudio/bookdown")
```

Remember each Rmd file contains one and only one chapter, and a chapter is defined by the first-level heading `#`.

To compile this example to PDF, you need XeLaTeX. You are recommended to install TinyTeX (which includes XeLaTeX): <https://yihui.name/tinytex/>.

```{r include=FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), 'bookdown', 'knitr', 'rmarkdown'
), 'packages.bib')
```

```{r setup, message=FALSE, warning=FALSE}
library(data.table)
library(tidyverse)
library(origami)
library(SuperLearner)
library(sl3)
library(ggplot2)
library(knitr)
library(kableExtra)

# load data set and take a peek
washb_data <- fread("https://raw.githubusercontent.com/tlverse/tlverse-data/master/wash-benefits/washb_data.csv",
                    stringsAsFactors = TRUE)
head(washb_data) %>%
  kable(digits = 4) %>%
  kableExtra:::kable_styling(fixed_thead = T) %>%
  scroll_box(width = "100%", height = "300px")
```


```{r task, debug = TRUE}
library(sl3)
# specify the outcome and covariates
outcome <- "whz"
covars <- colnames(washb_data)[-which(names(washb_data) == outcome)]

# create the sl3 task
debugonce(make_sl3_Task)
browser()
washb_task <- make_sl3_Task(
  data = washb_data,
  covariates = covars,
  outcome = outcome
)
```
